\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
Added information of theory of mind, completed to do for memory

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is 
involved in the perception of facial stimuli.\cite{IPL}

@@

The \textit{Theory of Mind} is a body of work in philosophy and psychology which
describes an individual's ability to consider the mental states of others, such as
appreciating another individual's false beliefs (knowledge based on incorrect or
outdated information). The Theory of Mind captures not only one's ability to
attribute beliefs, desires, and emotions to others but also to oneself --- and to
differentiate the two. \cite{autistictheoryofmind}

In addition to The Theory of Mind, the dmPFC is involved in empathy, moral reasoning,
and altruistic behavior. \cite{defaultnetworkadaptive,dmpfcothers,dmpfcaltruism}

@@

The DMN is also involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

\todo{expand on DMN involvement in past/future/stories. how does this work?}

@@

\bibitem{IPL}
 Radua J, Phillips ML, Russell T, Lawrence N, Marshall N, Kalidindi S, El-Hage W, McDonald C, 
 Giampietro V, Brammer MJ, David AS, Surguladze SA.
 \textit{Neural response to specific components of fearful faces in healthy 
  and schizophrenic adults.}
  Neuroimage. 2010 Jan 1;49(1):939-46. doi: 10.1016/j.neuroimage.2009.08.030. 
  Epub 2009 Aug 20.
  \url:https://www.ncbi.nlm.nih.gov/pubmed/19699306

@@

@@

>>>>

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is 
involved in the perception of facial stimuli. \cite{ipl}

@@

The \textit{Theory of Mind} is a body of work in philosophy and psychology which
describes an individual's ability to consider the mental states of others, such as
appreciating another individual's false beliefs (knowledge based on incorrect or
outdated information). The Theory of Mind captures not only one's ability to
attribute beliefs, desires, and emotions to others but also to oneself --- and to
differentiate the two. \cite{autistictheoryofmind}
There is a rich body of work pointing to this network (especially the dmPFC) being engaged
when individuals reflect upon, evaluate, appraise their own thoughts, feelings and desires 
as well as those of others. \cite{theoryofmind}

In addition to this, the dmPFC is involved in empathy, moral reasoning,
and altruistic behavior. \cite{defaultnetworkadaptive,dmpfcothers,dmpfcaltruism}

@@

The critical role of the medial temporal lobe (MTL) which is a part of the DMN 
in long term memory is well documented. \cite{mtl}
This network has also been activated during autobiographical memory retrieval, 
contextual association, and semantic knowledge. \cite{defaultnetworkadaptive}

It has been hypothesized that the adaptive role of memory retrieval is to facilitate 
construction of episodes to prepare for immediate and distant future scenarios.
So the DMN is involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

@@

\bibitem{ipl}
 Radua J, Phillips ML, Russell T, Lawrence N, Marshall N, Kalidindi S, El-Hage W, McDonald C, 
 Giampietro V, Brammer MJ, David AS, Surguladze SA.
 \textit{Neural response to specific components of fearful faces in healthy 
  and schizophrenic adults.}
  Neuroimage. 2010 Jan 1;49(1):939-46. doi: 10.1016/j.neuroimage.2009.08.030. 
  Epub 2009 Aug 20.
  \url:https://www.ncbi.nlm.nih.gov/pubmed/19699306

@@

\bibitem{theoryofmind}
  Frank Van Overwalle
 \textit{A dissociation between social mentalizing and general reasoning}
  NeuroImage. Volume 54, Issue 2, 15 January 2011, Pages 1589-1599
  \url:https://www.sciencedirect.com/science/article/abs/pii/S1053811910012243

@@

\bibitem{mtl}
 Scoville WB, Milner B
 \textit{Loss of recent memory after bilateral hippocampal lesions.}
  J Neurol Neurosurg Psych,  1957;20:11–21.
